|

### 2022-09-26 paper_comparison/paper_comparison/paper_comparison.Rmd
shorten the data preprocessing

```{r get-lineup-data}
if (!file.exists(here::here("data/third_study/polynomials_lineup.rds"))) {
  polynomials_lineup <- get_polynomials_lineup()
  saveRDS(polynomials_lineup, here::here("data/third_study/polynomials_lineup.rds"))
} else {
  polynomials_lineup <- readRDS(here::here("data/third_study/polynomials_lineup.rds"))
}

if (!file.exists(here::here("data/fourth_study/heter_lineup.rds"))) {
  heter_lineup <- get_polynomials_lineup()
  saveRDS(heter_lineup, here::here("data/fourth_study/heter_lineup.rds"))
} else {
  heter_lineup <- readRDS(here::here("data/fourth_study/heter_lineup.rds"))
}
```

```{r get-conv-result}
stand_dist <- function(x) (x - min(x))/max(x - min(x)) * 2 - 1

if (!file.exists(here::here("data/third_study/conv_result.rds"))) {
  conv_result <- list()
  for (i in 1:100)
  {
    conv_result[[i]] <- map(1:2000,
                            function(x) {
                     shape <- sample(1:4, 1)
                     e_sigma <- sample(c(0.5, 1, 2, 4), 1)
                     x_dist <- sample(c("uniform", "normal", "lognormal", "even_discrete"), 1)
                     x <- switch(x_dist,
                                 uniform = rand_uniform(-1, 1),
                                 normal = {raw_x <- rand_normal(sigma = 0.3); closed_form(~stand_dist(raw_x))},
                                 lognormal = {raw_x <- rand_lognormal(sigma = 0.6); closed_form(~stand_dist(raw_x/3 - 1))},
                                 even_discrete = rand_uniform_d(k = 5, even = TRUE))
                     mod <- poly_model(shape, x = x, sigma = e_sigma)
                     n <- sample(c(50, 100, 300), 1)
                     tmp_dat <- mod$gen(n)

                     tibble(shape = shape,
                            e_sigma = e_sigma,
                            x_dist = x_dist,
                            n = n,
                            effect_size = mod$effect_size(tmp_dat),
                            p_value = mod$test(tmp_dat)$p_value,
                            reject = p_value < 0.05,
                            boot_id = i)
                   }) %>%
  reduce(bind_rows) %>%
  mutate(reject = as.numeric(reject))
  }

  conv_result <- conv_result %>%
    reduce(bind_rows)

  saveRDS(conv_result, here::here("data/third_study/conv_result.rds"))
} else {
  conv_result <- readRDS(here::here("data/third_study/conv_result.rds"))
}

@@

if (!file.exists(here::here("data/fourth_study/conv_result_heter.rds"))) {
  conv_result_heter <- list()
  for (i in 1:100)
  {
    conv_result_heter[[i]] <- map(1:2000,
                            function(x) {
                     a <- sample(c(-1, 0, 1), 1)
                     b <- sample(c(0.25, 1, 4, 16, 64), 1)
                     x_dist <- sample(c("uniform", "normal", "lognormal", "even_discrete"), 1)
                     x <- switch(x_dist,
                                 uniform = rand_uniform(-1, 1),
                                 normal = {raw_x <- rand_normal(sigma = 0.3); closed_form(~stand_dist(raw_x))},
                                 lognormal = {raw_x <- rand_lognormal(sigma = 0.6); closed_form(~stand_dist(raw_x/3 - 1))},
                                 even_discrete = rand_uniform_d(-1, 1, k = 5, even = TRUE))
                     mod <- heter_model(a = a, b = b, x = x)
                     n <- sample(c(50, 100, 300), 1)
                     tmp_dat <- mod$gen(n)

                     tibble(a = a,
                            b = b,
                            x_dist = x_dist,
                            n = n,
                            effect_size = mod$effect_size(tmp_dat, type = "kl"),
                            p_value = mod$test(tmp_dat)$p_value,
                            reject = p_value < 0.05,
                            boot_id = i)
                   }) %>%
  reduce(bind_rows) %>%
  mutate(reject = as.numeric(reject))
  }

  conv_result_heter <- conv_result_heter %>%
    reduce(bind_rows)

  saveRDS(conv_result_heter, here::here("data/fourth_study/conv_result_heter.rds"))
} else {
  conv_result_heter <- readRDS(here::here("data/fourth_study/conv_result_heter.rds"))
}

@@

if (!file.exists(here::here("data/fourth_study/conv_result_heter_SW.rds"))) {
  conv_result_heter_SW <- list()
  for (i in 1:100)
  {
    conv_result_heter_SW[[i]] <- map(1:2000,
                            function(x) {
                     a <- sample(c(-1, 0, 1), 1)
                     b <- sample(c(0.25, 1, 4, 16, 64), 1)
                     x_dist <- sample(c("uniform", "normal", "lognormal", "even_discrete"), 1)
                     x <- switch(x_dist,
                                 uniform = rand_uniform(-1, 1),
                                 normal = {raw_x <- rand_normal(sigma = 0.3); closed_form(~stand_dist(raw_x))},
                                 lognormal = {raw_x <- rand_lognormal(sigma = 0.6); closed_form(~stand_dist(raw_x/3 - 1))},
                                 even_discrete = rand_uniform_d(-1, 1, k = 5, even = TRUE))
                     mod <- heter_model(a = a, b = b, x = x)
                     n <- sample(c(50, 100, 300), 1)
                     tmp_dat <- mod$gen(n)

                     tibble(a = a,
                            b = b,
                            x_dist = x_dist,
                            n = n,
                            effect_size = mod$effect_size(tmp_dat, type = "kl"),
                            p_value = shapiro.test(tmp_dat$.resid)$p.value,
                            reject = p_value < 0.05,
                            boot_id = i)
                   }) %>%
  reduce(bind_rows) %>%
  mutate(reject = as.numeric(reject))
  }

  conv_result_heter_SW <- conv_result_heter_SW %>%
    reduce(bind_rows)

  saveRDS(conv_result_heter_SW, here::here("data/fourth_study/conv_result_heter_SW.rds"))
} else {
  conv_result_heter_SW <- readRDS(here::here("data/fourth_study/conv_result_heter_SW.rds"))
}

```{r}
if (!file.exists(here::here("data/third_study/wrong_BP_conv_result.rds"))) {
  wrong_BP_conv_result <- list()
  for (i in 1:100)
  {
    wrong_BP_conv_result[[i]] <- map(1:2000,
                            function(x) {
                     shape <- sample(1:4, 1)
                     e_sigma <- sample(c(0.5, 1, 2, 4), 1)
                     x_dist <- sample(c("uniform", "normal", "lognormal", "even_discrete"), 1)
                     x <- switch(x_dist,
                                 uniform = rand_uniform(-1, 1),
                                 normal = {raw_x <- rand_normal(sigma = 0.3); closed_form(~stand_dist(raw_x))},
                                 lognormal = {raw_x <- rand_lognormal(sigma = 0.6); closed_form(~stand_dist(raw_x/3 - 1))},
                                 even_discrete = rand_uniform_d(k = 5, even = TRUE))
                     mod <- poly_model(shape, x = x, sigma = e_sigma)
                     n <- sample(c(50, 100, 300), 1)
                     tmp_dat <- mod$gen(n)

                     tibble(shape = shape,
                            e_sigma = e_sigma,
                            x_dist = x_dist,
                            n = n,
                            effect_size = mod$effect_size(tmp_dat),
                            p_value = HETER_MODEL$test(tmp_dat)$p_value,
                            reject = p_value < 0.05,
                            boot_id = i)
                   }) %>%
  reduce(bind_rows) %>%
  mutate(reject = as.numeric(reject))
  }

  wrong_BP_conv_result <- wrong_BP_conv_result %>%
    reduce(bind_rows)

  saveRDS(wrong_BP_conv_result, here::here("data/third_study/wrong_BP_conv_result.rds"))
} else {
  wrong_BP_conv_result <- readRDS(here::here("data/third_study/wrong_BP_conv_result.rds"))
}

```{r}
if (!file.exists(here::here("data/third_study/wrong_SW_conv_result.rds"))) {
  wrong_SW_conv_result <- list()
  for (i in 1:100)
  {
    wrong_SW_conv_result[[i]] <- map(1:2000,
                            function(x) {
                     shape <- sample(1:4, 1)
                     e_sigma <- sample(c(0.5, 1, 2, 4), 1)
                     x_dist <- sample(c("uniform", "normal", "lognormal", "even_discrete"), 1)
                     x <- switch(x_dist,
                                 uniform = rand_uniform(-1, 1),
                                 normal = {raw_x <- rand_normal(sigma = 0.3); closed_form(~stand_dist(raw_x))},
                                 lognormal = {raw_x <- rand_lognormal(sigma = 0.6); closed_form(~stand_dist(raw_x/3 - 1))},
                                 even_discrete = rand_uniform_d(k = 5, even = TRUE))
                     mod <- poly_model(shape, x = x, sigma = e_sigma)
                     n <- sample(c(50, 100, 300), 1)
                     tmp_dat <- mod$gen(n)

                     tibble(shape = shape,
                            e_sigma = e_sigma,
                            x_dist = x_dist,
                            n = n,
                            effect_size = mod$effect_size(tmp_dat),
                            p_value = shapiro.test(tmp_dat$.resid)$p.value,
                            reject = p_value < 0.05,
                            boot_id = i)
                   }) %>%
  reduce(bind_rows) %>%
  mutate(reject = as.numeric(reject))
  }

  wrong_SW_conv_result <- wrong_SW_conv_result %>%
    reduce(bind_rows)

  saveRDS(wrong_SW_conv_result, here::here("data/third_study/wrong_SW_conv_result.rds"))
} else {
  wrong_SW_conv_result <- readRDS(here::here("data/third_study/wrong_SW_conv_result.rds"))
}

@@

@@

>>>>

```{r get-lineup-data}
if (!file.exists(here::here("data/vi_lineup.rds"))) {
  vi_lineup <- get_vi_lineup()
  saveRDS(vi_lineup, here::here("data/vi_lineup.rds"))
} else {
  vi_lineup <- readRDS(here::here("data/vi_lineup.rds"))
}
```

@@

if (!file.exists(here::here("data/poly_conventional_simulation.rds"))) {
  poly_conv_sim <- list()
  for (i in 1:100)
  {
    poly_conv_sim[[i]] <- map(1:2000,
                            function(x) {
                     shape <- sample(1:4, 1)
                     e_sigma <- sample(c(0.5, 1, 2, 4), 1)
                     x_dist <- sample(c("uniform", "normal", "lognormal", "even_discrete"), 1)
                     x <- switch(x_dist,
                                 uniform = rand_uniform(-1, 1),
                                 normal = {raw_x <- rand_normal(sigma = 0.3); closed_form(~stand_dist(raw_x))},
                                 lognormal = {raw_x <- rand_lognormal(sigma = 0.6); closed_form(~stand_dist(raw_x/3 - 1))},
                                 even_discrete = rand_uniform_d(k = 5, even = TRUE))
                     mod <- poly_model(shape, x = x, sigma = e_sigma)
                     n <- sample(c(50, 100, 300), 1)
                     tmp_dat <- mod$gen(n)

                     tibble(shape = shape,
                            e_sigma = e_sigma,
                            x_dist = x_dist,
                            n = n,
                            effect_size = mod$effect_size(tmp_dat),
                            F_p_value = mod$test(tmp_dat)$p_value,
                            BP_p_value = HETER_MODEL$test(tmp_dat)$p_value,
                            SW_p_value = shapiro.test(tmp_dat$.resid)$p.value,
                            boot_id = i)
                   }) %>%
  reduce(bind_rows)
  }

  poly_conv_sim <- poly_conv_sim %>%
    reduce(bind_rows)

  saveRDS(poly_conv_sim, here::here("data/poly_conventional_simulation.rds"))
} else {
  poly_conv_sim <- readRDS(here::here("data/poly_conventional_simulation.rds"))
}
```

@@

if (!file.exists(here::here("data/heter_conventional_simulation.rds"))) {
  heter_conv_sim <- list()
  for (i in 1:100)
  {
    heter_conv_sim[[i]] <- map(1:2000,
                            function(x) {
                     a <- sample(c(-1, 0, 1), 1)
                     b <- sample(c(0.25, 1, 4, 16, 64), 1)
                     x_dist <- sample(c("uniform", "normal", "lognormal", "even_discrete"), 1)
                     x <- switch(x_dist,
                                 uniform = rand_uniform(-1, 1),
                                 normal = {raw_x <- rand_normal(sigma = 0.3); closed_form(~stand_dist(raw_x))},
                                 lognormal = {raw_x <- rand_lognormal(sigma = 0.6); closed_form(~stand_dist(raw_x/3 - 1))},
                                 even_discrete = rand_uniform_d(-1, 1, k = 5, even = TRUE))
                     mod <- heter_model(a = a, b = b, x = x)
                     n <- sample(c(50, 100, 300), 1)
                     tmp_dat <- mod$gen(n)

                     tibble(a = a,
                            b = b,
                            x_dist = x_dist,
                            n = n,
                            effect_size = mod$effect_size(tmp_dat, type = "kl"),
                            F_p_value = POLY_MODEL$test(mutate(tmp_dat, z = poly_model()$gen(n, computed = select(tmp_dat, x))$z))$p_value,
                            BP_p_value = mod$test(tmp_dat)$p_value,
                            SW_p_value = shapiro.test(tmp_dat$.resid)$p.value,
                            boot_id = i)
                   }) %>%
  reduce(bind_rows)
  }

  heter_conv_sim <- heter_conv_sim %>%
    reduce(bind_rows)

  saveRDS(heter_conv_sim, here::here("data/heter_conventional_simulation.rds"))
} else {
  heter_conv_sim <- readRDS(here::here("data/heter_conventional_simulation.rds"))
}
```

@@

<!-- residual plot -> plot -->

<!-- plot a included -->

@@

<!-- adam work -->
